IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-18 paper/retrofit.tex
doom

For our first example, here is a program which spawns a new isolated task,
and then sends it a mutable reference:
\begin{align*}
    & |let i = TI (sandbox (brecvf x _ (IT (!(TI x)))))|\\
    & |in TI (send (IT i) l (IT (ref true)))|
\end{align*}
For now, ignore the tags |TI| and |IT|: roughly, this code creates a new
|sandbox|ed task with identifier $i$ which waits (\textbf{blockingRecv}, binding $x$ with the received message) for a
message, and then \textbf{send}s the task a mutable reference |(ref
true)| which it labels $l$.  If this operation actually shared the mutable cell between the two tasks, it
could be used to violate information flow control if the tasks had differing labels.  At this point, the designer of an IFC system might add label checks to mutable references, to check the labels of the reader and writer---solving the leak, but also dooming the performance of mutable references in the system.

@@

\begin{figure}
\begin{tabular}{ll}
\begin{minipage}{.45\textwidth}
\begin{code}
  roundrobin step (it1, it2, ldots)    = it2, ldots, it1
  roundrobin done (it1, it2, ldots)    = it2, ldots
  roundrobin nostep (it1, it2, ldots)  = it2, ldots
  roundrobin box (it1, it2, ldots)     = it2, ldots, it1
\end{code}
\end{minipage} &
\begin{minipage}{.45\textwidth}
\begin{code}
  seq step (it1, it2, ldots)      = it1, it2, ldots
  seq nostep (it1, it2, ldots)    = it1, it2, ldots
  seq done (it)                   = it
  seq done (it1, it2, ldots)      = it2, ldots
  seq box (it1, it2, ldots, itn)  = itn, it1, it2, ldots
\end{code}
\end{minipage}
\end{tabular}
\caption{Scheduling policies (concurrent round robin on the left, sequential on the right).}
\label{fig:scheduler}
\end{figure}

>>>>

For our first example, here is a program which spawns a new isolated task,
and then sends it a mutable reference:
\begin{align*}
    & |let i = TI (sandbox (brecvf x _ (IT (!(TI x)))))|\\
    & |in TI (send (IT i) l (IT (ref true)))|
\end{align*}
For now, ignore the tags |TI| and |IT|: roughly, this code creates a new
|sandbox|ed task with identifier $i$ which waits (\textbf{blockingRecv}, binding $x$ with the received message) for a
message, and then \textbf{send}s the task a mutable reference |(ref
true)| which it labels $l$.  If this operation actually shared the mutable cell between the two tasks, it
could be used to violate information flow control if the tasks had
differing labels.  At this point, the designer of an IFC system might
add label checks to mutable references, to check the labels of the
reader and writer. While this solves the leak, for languages like
JavaScript, where references are prevalently used, this also dooms the
performance of the system.

@@

\begin{figure}
\begin{tabular}{ll}
\begin{minipage}{.45\textwidth}
\begin{code}
  roundrobin step (it1, it2, ldots)    = it2, ldots, it1
  roundrobin done (it1, it2, ldots)    = it2, ldots
  roundrobin nostep (it1, it2, ldots)  = it2, ldots
  roundrobin box (it1, it2, ldots)     = it2, ldots, it1
\end{code}
\end{minipage} &
\begin{minipage}{.45\textwidth}
\begin{code}
  seq step (it1, it2, ldots)      = it1, it2, ldots
  seq nostep (it1, it2, ldots)    = it1, it2, ldots
  seq done (it)                   = it
  seq done (it1, it2, ldots)      = it2, ldots
  seq box (it1, it2, ldots, itn)  = itn, it1, it2, ldots
\end{code}
\end{minipage}
\end{tabular}
\vspace*{-0.5cm}
\caption{Scheduling policies (concurrent round robin on the left, sequential on the right).}
\label{fig:scheduler}
\end{figure}
